UGrade: Autograder for Competitive Programming Using Contestant PC as Worker

### 2019-11-02 src/paper.tex
remove popular claim

Competitive programming is one of the most popular competitions in the computer science field. In competitive programming competition, contestants are asked to solve computer science problems correctly and as fast as possible. Some institutes and organizations often organize competitive programming competition periodically. Some big companies like Google and Facebook organize competitive programming competition annually. Competitive programming competition is supported by an online judge system. Usually, online judge system is a web-based application where contestants can read the problems, create clarifications, submit their solution, and watch the scoreboard. Currently, the most popular online judges are Codeforces, URI Online Judge \cite{uriojpaper}, Uva, and SPOJ.

@@

There are some popular online judge systems that have been used to organize competitive programming competition. Some online judges offer other additional features like discussion forum, training gate, and rating system. Nowadays, most of the online judges are deployed as a web application and use a specific computer to grade contestants' submissions. There are many types of competitive programming competition rules. Most of the online judges only support a specific competition rule.

One of the most popular competitive programming competition is ACM-ICPC (icpc.baylor.edu) competition where the competition uses ICPC rules. In ACM-ICPC competition, contestants compete in a group of three people. Every group has the same amount of problems to solve, and the score is determined by the number of solved problem and time penalty. There are many online judges that support this competitive programming rule. The most popular online judge that support this type of competition is DOMJudge. DOMJudge is very popular because it has many useful features, easy to use and open source.

@@

The grading performance between UGrade and DOMJudge was compared. DOMJudge was choosen as the comparison because it was the most popular open source online judge system for ICPC competition. UGrade and DOMJudge were deployed in a computer with the same specification. Then fifteen computers were deployed to simulating the contestant actions. For DOMJudge, two more computers were deployed to work as the autograder worker. For UGrade, the fifteen computers worked as workers.

@@

Based on the development and testing that have been done, there are some lessons that can be learned.
\begin{enumerate}
    \item There is a high grading performance improvement in UGrade compared to many online judges that are currently popular. This performance improvement is caused by the number of the worker in the UGrade which follows the number of contestants in the competition.
    \item The grading performance of UGrade is not affected by the number of contestants but affected by the grading size number of UGrade. The high number of contestant causes a high number of worker too, so that does not affect the grading performance. However, the grading size number causes the number of submission doubles, thus affects the grading performance.
    \item The high number of grading size reduces grading performance but increases system security. The low number of grading size increases grading performance but reduces system security. The juries need to adjust the grading size to achieve the best result.
    \item UGrade can keep the fairness of grading process even if the worker computers have different specification and performance. UGrade achieves this by comparing the jury's solution and contestant's solution in the same computer.
\end{enumerate}

>>>>

Competitive programming is a one type of competitions in the computer science field. In competitive programming competition, contestants are asked to solve computer science problems correctly and as fast as possible. Some institutes and organizations often organize competitive programming competition periodically. Some big companies like Google and Facebook organize competitive programming competition annually. Competitive programming competition is supported by an online judge system. Usually, online judge system is a web-based application where contestants can read the problems, create clarifications, submit their solution, and watch the scoreboard. Currently, there are some widely known online judges such as Codeforces, URI Online Judge \cite{uriojpaper}, Uva, and SPOJ.

@@

There are some online judge systems that have been widely used to organize competitive programming competition. Some online judges offer other additional features like discussion forum, training gate, and rating system. Nowadays, most of the online judges are deployed as a web application and use a specific computer to grade contestants' submissions. There are many types of competitive programming competition rules. Most of the online judges only support a specific competition rule.

One of the most widely known competitive programming competition is ACM-ICPC (icpc.baylor.edu) competition where the competition uses ICPC rules. In ACM-ICPC competition, contestants compete in a group of three people. Every group has the same amount of problems to solve, and the score is determined by the number of solved problem and time penalty. There are many online judges that support this competitive programming rule. One of the online judges that support this type of competition is DOMJudge. DOMJudge is used in ACM-ICPC world final because it has many useful features, easy to use and open source.

@@

The grading performance between UGrade and DOMJudge was compared. DOMJudge was choosen as the comparison because it is open source and has been used in many competitive programming competitions. UGrade and DOMJudge were deployed in a computer with the same specification. Then fifteen computers were deployed to simulating the contestant actions. For DOMJudge, two more computers were deployed to work as the autograder worker. For UGrade, the fifteen computers worked as workers.

@@

Based on the development and testing that have been done, there are some lessons that can be learned.
\begin{enumerate}
    \item There is a high grading performance improvement in UGrade compared to many online judges that  currently exists. This performance improvement is caused by the number of the worker in the UGrade which follows the number of contestants in the competition.
    \item The grading performance of UGrade is not affected by the number of contestants but affected by the grading size number of UGrade. The high number of contestant causes a high number of worker too, so that does not affect the grading performance. However, the grading size number causes the number of submission doubles, thus affects the grading performance.
    \item The high number of grading size reduces grading performance but increases system security. The low number of grading size increases grading performance but reduces system security. The juries need to adjust the grading size to achieve the best result.
    \item UGrade can keep the fairness of grading process even if the worker computers have different specification and performance. UGrade achieves this by comparing the jury's solution and contestant's solution in the same computer.
\end{enumerate}
